Delaying Bug Fixes is a Bad Idea?

### 2015-07-30 phaseDelay.tex

\conferenceinfo{ICSE}{'16 Austin, Texas}
\title{Are Older Bugs More Expensive to Fix that Newer Bugs? }
\numberofauthors{3}
\author{
%\alignauthor 
Tim Menzies \\
       \affaddr{Computer Science}\\
       \affaddr{NC State University, USA}\\
       \email{tim.menzies@gmail.com}
\and%alignauthor 
William Nichols, Forest Shull \\
        \affaddr{Software Engineering Institute}\\
        \affaddr{Carnegie Mellon U, USA}\\
        \email{\{wrn,fjshull\}@sei.cmu.edu} 
\and %\alignauthor 
Lucas Layman \\
       \affaddr{Fraunhofer CESE} \\
       \affaddr{College Park, USA}\\ 
       \email{llayman@fc-md.umd.edu}
} 
\maketitle
\begin{abstract}
Does
repair time increase dramatically
the longer an issue persists in a system?
Many industrial practitioners and academics this   to be true.
This   belief is used to justify 
major investments in  software development
 processes and methods.

@@

comment on why post is no longer current. continuous deployment. package managers.Windows moving from service patches (which occur rarely) to continuous deployment (so there will be no windows 11... just a stream of continuous updates).   architectural incubators: big superstructures within which it is simpler and cheaper to do many small projects. e.g. aircraft carriers,  packet-stitching. mean stack (to be clear: none of the data explored in this paper comes from such architectural incubators: this paragraph is only meant to be a  speculation of future implications of this old data to newer projects).

@@

@@

\section*{Acknowledgements}
This work was partially funded by an National Science
Foundation grants NSF-CISE 1302169 and CISE 1506586.
\\
We thank Tuma Solutions for providing the Team Process Data Warehouse software in support of this research.  \\
Personal Software Process$\textsuperscript{SM}$, Team Software Process$\textsuperscript{SM}$, and TSP$\textsuperscript{SM}$ are service marks of Carnegie Mellon University.

>>>>

\conferenceinfo{ICSE}{'16 Austin, Texas}
\title{Delaying Bug Fixes is a Bad Idea?}
\numberofauthors{3}
\author{
%\alignauthor 
Tim Menzies \\
       \affaddr{Computer Science}\\
       \affaddr{NC State University, USA}\\
       \email{tim.menzies@gmail.com}
\and%alignauthor 
William Nichols, Forest Shull \\
        \affaddr{Software Engineering Institute}\\
        \affaddr{Carnegie Mellon U, USA}\\
        \email{\{wrn,fjshull\}@sei.cmu.edu} 
\and %\alignauthor 
Lucas Layman \\
       \affaddr{Fraunhofer CESE} \\
       \affaddr{College Park, USA}\\ 
       \email{llayman@fc-md.umd.edu}
} 
\maketitle
\begin{abstract}
Does
repair time increase dramatically
the longer an issue persists in a system?
Many industrial practitioners and academics this   to be true.
This   belief is used to justify 
major investments in  software development
 processes and methods.

@@

comment on why post is no longer current. continuous deployment. package managers.Windows moving from service patches (which occur rarely) to continuous deployment (so there will be no windows 11... just a stream of continuous updates~\cite{bright15}).   architectural incubators: big superstructures within which it is simpler and cheaper to do many small projects. e.g. aircraft carriers,  packet-stitching. mean stack (to be clear: none of the data explored in this paper comes from such architectural incubators: this paragraph is only meant to be a  speculation of future implications of this old data to newer projects).

\begin{figure}
{\small
\begin{center}
\begin{tabular}{r|rrrr|r}
& \multicolumn{4}{c}{Phase Requirements Issue Found }& ref\\
                &Requirements & Design & Code&  Test& ref\\\hline
 & 1& 5& 10& 50&~\cite{Boehm81}\\  
& 1 &3& 5& 37&?\\ 
&  1 &3& 7& 51& ?\\ 
& 1& 5 &33 &75& ? \\
& 1  &    & 10 & 40& ?\\ 
& 1   &    & 10 &  40& ?\\
&  1 & 20 & 45 & 250& ?\\  
&  1  &   5 &      & 50& ? \\\hline
mean             & 1 & 7.3 & 25.6 & 177\\
median           & 1 &  5  & 10   & 50.5 
\end{tabular}
\end{center}}
\caption{Sample of the Stecklein et al. literature; from~\cite{steck04}.}
\end{figure}

\begin{figure}
{\small\begin{center} \begin{tabular}{r|rrr}
& method1 & method2 & method3\\\hline
requirements& 1& 1 & 1 \\
design& 8 & 4 & 1\\
build& 16 & 16 & 7\\
test& 21 & 78 & 28\\
operation& 29 & 186 & 1615
\end{tabular}\end{center} }
\caption{Results from the   Stecklein et al. study~\cite{steck04}.}
\end{figure}

Method1 linear ($R^2$ == 99\%).

\begin{figure}[!t] 
%\vspace{-1cm}
%\hspace{-0.35in}
\begin{center}
\includegraphics[width=3in]{img/b81.pdf}
 \end{center}
% ~\\~\\
%~\\~\\~\\

@@

\subsection{Future Work}
There is another ``phase delay'' effect, not discussed above. Even if software is readily updatable, there   may be a ``user phase delay''   amongst   humans using that software.

Changes to  software that is used by a large population can be confusing (particularly for the sick or elderly). 
Consider the 23,000,000 veterans working with  the U.S.  Veterans 
Administration (VA) service. Some of those veterans are dependent on health care or pensions from the VA. Those veterans use the VA's web interfaces
to  (e.g.) find out
when their next cheque will arrive. Before we can update the VA web software, we would
need to  a transition plan that helps users   move from the older to the newer system. This is an example of what might be called a ``user phase delay''; i.e. changes to software are more complex to process, particularly if some users have styled
their day-to-day work flow around the services offered by the older software.

This issue of ``user phase delay'' is not addressed by our data, nor by the prior studies on phase delay discussed above.  Hence, this issues   is out of scope for this paper since the expectation that ``older bugs cost more to fix than newer bugs'' was not formed around 
user issues.

That said,  
we think that ``user phase delay'' will become a bigger issue in the future when more people are using more software as part of their day to day life. We even envision a time when users demand fewer updates, just to offer some stability in their life. This is a matter for future work.

@@

\section*{Acknowledgements}
The authors gratefully acknowledge the careful comments of anonymous reviewers-- particularly, their comments on issues relating to ``cost''
and ``time''.
This work was partially funded by an National Science
Foundation grants NSF-CISE 1302169 and CISE 1506586.
\\
We thank Tuma Solutions for providing the Team Process Data Warehouse software in support of this research.  \\
Personal Software Process$\textsuperscript{SM}$, Team Software Process$\textsuperscript{SM}$, and TSP$\textsuperscript{SM}$ are service marks of Carnegie Mellon University.
